---
title: "Jazz through the years"
author: "Jonas Schoonhoven"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(usethis)
library(spotifyr)
library(compmus)
library(plotly)
```

### Self similar but not the same [chroma and Timbre]
```{r data self_similarity}
sinatra <-
  get_tidy_audio_analysis("4FmCUATNIarCQh72JYdvnm") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

buble <-
  get_tidy_audio_analysis("7wgYqjzA3qJLpyz89IlVPA") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

dennis <-
  get_tidy_audio_analysis("2Eq65QUisMmXt5StcQCMij") |> # Change URI.
  compmus_align(bars, segments) |>                     # Change `bars`
  select(bars) |>                                      #   in all three
  unnest(bars) |>                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) |>
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )
```


```{r, self-similarity}
sinatra |>
  compmus_self_similarity(timbre, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "", title = "Sinatra - That's life" )

buble |>
  compmus_self_similarity(timbre, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "", title = "Buble - That's life")

dennis |>
  compmus_self_similarity(timbre, "cosine") |> 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "", y = "", title = "van Aarsen - That's life")
```

***

Interesting to see the that the three iterations of this song have different places of being different compared to itself.

I'm going to try and improve the layout of these 3 plots in the future. Because even I can see right now this is design wise horrible. 


### Desciption of Corpus

I have chosen a corpus containing in total 120 tracks (could become more in the future). The foundation of the corpus exists of two playlists combined, supplemented with around twenty tracks. The two playlists I used were the "This is Michael Buble" and the "This is Frank Sinatra" playlists. In other words JAZZZZZ. When you've listened to Buble before you may be familliar with the fact that Buble has many covers in his audiography. A lot of covers are also songs of Sinatra. I'm interested to see if there are any similarities between the two artists or that Buble reinvented the songs by giving his own twist to the lyrics.

My natural groups of comparison points in my corpus are (of course) the artists and their genres. I am gonna try to think of a few more comparison points but for now i will stick to these two. I expect that there will be a lot of similarities between the two artists, but at the same time i expect there to be different interpretations of the same songs by the two artists.

I think my corpus is generally representative of the points I want to compare. Because of the amount of covers Buble has produced in his career there are a lot of songs to compare. However, I do think there are a healthy amount of outliers with respect to the songs of Buble, because not ALL his songs are of the genre Jazz.

A track I think is typical in my corpus is the classic: Fly me to the moon. There are an unthinkable amount of covers made of this song. I am excited to research the similarities or differences the artists made during their interpretation of this song.

### Made Buble the genre more danceable? 

```{r scatterplot}
jazz <- get_playlist_audio_features("", "6W4qNJv2ViwlCElxMIK24H")
MB <- get_playlist_audio_features("", "37i9dQZF1DZ06evO0WqnZe")
FS <- get_playlist_audio_features("", "37i9dQZF1DZ06evO102dNu")
combined <- rbind(MB, FS)

scatter <- ggplot(combined, aes(x=valence, y=danceability, color=playlist_name)) +
  geom_point() +
  geom_smooth(se=FALSE, linewidth = 0.5) +
  expand_limits(x=0, y=0) +
  labs(x="Valence", y="Danceability")

ggplotly(scatter) %>%
  layout(legend = list(x=0.7, y=0.1))
```

***

I have made a scatterplot with on the x axis all the valence values of the tracks that are present in the "This is Frank Sinatra" and "This is Micheal Buble" playlists. On the y axis i have plotted al the danceability values of the same tracks. For the color of the dots I have used the album of the artist who sang the song. This makes it clear which dot belongs to which artist. 

I think this plot is interesting because it is actually in line with what I thought about the artist before making the plot. In the plot it can be seen that Buble in general scores higher in the danceability scores than Sinatra. My thoughts about the bibliograhpy of Buble were that he has a lot covers from Sinatra and next to those covers he has more hip hop styled songs. I think that these thoughts are well represented in this plot.

### Same song, same interpretation [chroma features]

```{r DTW}
sinatra <-
  get_tidy_audio_analysis("7FXj7Qg3YorUxdrzvrcY25") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

buble <-
  get_tidy_audio_analysis("7rqSxhVpV4uSKI6WBuToC7") |>
  select(segments) |>
  unnest(segments) |>
  select(start, duration, pitches)

compmus_long_distance(
  sinatra |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  buble |> mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  feature = pitches,
  method = "euclidean"
) |>
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_equal() +
  labs(x = "Sinatra", y = "Buble", title = "'Fly me to the moon' by two artits") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_fill_viridis_c(guide = NULL)
```

***

I really tried to make this plot interactive but my computer would literally crash.

### Keygrams

```{r data_keygrams}
circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )
```

```{r}
buble_told <-
  get_tidy_audio_analysis("7EBAGLLkK2qdtwZ0l1bOnV") |>
  compmus_align(sections, segments) |>
  select(sections) |>
  unnest(sections) |>
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "mean", norm = "manhattan"
      )
  )

buble_told |> 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) |>
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "", title="Have I told you that I love you - Buble")
```


### Conclusion

```{r}

```
